### 2015-05-08 paper/review-progress.Rmd
added luke's comments to revision progress file

>>>>

From Luke

- The $200T figure only makes since as a cumulative figure (current world GDP is ~$50T) over many, many years. I suspect the OECD extrapolated out to infinity to get this number and the confidence interval is very wide.
- The association between the number of books in the home has been well documented and is well known. Our results simply corroborate the known association between ownership of certain household items and test scores.
- Also, the most critical reviewer seems very skeptical of survey statistics. The weighting scheme used accounts for non-response as is the case for any well-designed surveys. Does he/she want just want approximate percentages?
- The OECD is only able to survey students. So women deprived of educational opportunities are not in the sampling frame. Our analysis indicates, that for Jordan and Qatar, there is evidence of girls/women outperforming boys in math and reading.
- The visual plots seem like they would be much more informative regarding "scale" and "clinical differences" than raw numbers.
